### 2020-06-22 manuscript/report_technical_appendix.Rmd
add blink window parameter

Input: x-coordinate, y-coordinate, timestamp, unit of coordinates (px vs. deg), screen resolution, screen dimensions, distance to screen, sampling rate, blink indicator, order of SG filter, length of SG filter, number of states in the HMM, start values for the HMM, downsampling factor, random response start values, seed for random response start values, control options for fitting the HMM, minimum saccade duration.

@@

(@) The algorithm checks whether samples are valid: Samples for which the x- or y-coordinates are NA, infinity, or (0,0) are marked (internally) as invalid.
(@) Samples that match the blink indicator are labeled as blinks.
(@) If the unit is px, the x- and y-coordinates are transformed into va with: 
    i. The coordinates are centered ([0,0] is center)
    ii. $\theta_{deg} = atan(\frac{x \cdot res_x}{d_{screen} \cdot dim_x})\frac{180}{\pi}$
(@) Samples that are outside the screen are marked as invalid.
(@) Velocities and accelerations for the x- and y-coordiantes are calculated using an SG filter (3rd order, length = 5).
(@) Combined velocitiy and acceleration are calculated as: $v = f \sqrt{v_x^2 + v_y^2}$ and $a = f \sqrt{a_x^2 + a_y^2}$, with $f$ as the sampling rate. Note that acceleration is only multiplied by the sampling rate once. The second multiplication is done during postprocessing.
(@) Velocity and acceleration of value zero are nudged to be 0.01.
(@) Samples with velocity above 1000 deg/s or acceleration above 100 deg/s are marked as invalid.
(@) The sample-to-sample angle is calculated as: 
$$\theta_t = atan2(\frac{y_{t+1} - y_t}{x_{t+1} - x_t}) - atan2(\frac{y_t - y_{t-1}}{x_t - x_{t-1}}).$$ 
Angles are normalized to $[0,2\pi]$ by adding $2\pi$ to negative values.
(@) Samples that have an angle with value NA are marked as invalid.
(@) The velocity, acceleration, and angle of invalid samples are set to NA.

>>>>

Input: x-coordinate, y-coordinate, timestamp, unit of coordinates (px vs. deg), screen resolution, screen dimensions, distance to screen, sampling rate, blink indicator, blink window, order of SG filter, length of SG filter, number of states in the HMM, start values for the HMM, downsampling factor, random response start values, seed for random response start values, control options for fitting the HMM, minimum saccade duration.

@@

(@) The algorithm checks whether samples are valid: Samples for which the x- or y-coordinates are NA, infinity, or (0,0) are marked (internally) as invalid.
(@) Samples that match the blink indicator are labeled as blinks.
(@) All samples within +/- *blinkwindow* around blink indicated samples are marked as invalid and labeled as blinks.
(@) If the unit is px, the x- and y-coordinates are transformed into va with: 
    i. The coordinates are centered ([0,0] is center)
    ii. $\theta_{deg} = atan(\frac{x \cdot res_x}{d_{screen} \cdot dim_x})\frac{180}{\pi}$
(@) Samples that are outside the screen are marked as invalid.
(@) Velocities and accelerations for the x- and y-coordiantes are calculated using an SG filter (3rd order, length = 5).
(@) Combined velocitiy and acceleration are calculated as: $v = f \sqrt{v_x^2 + v_y^2}$ and $a = f \sqrt{a_x^2 + a_y^2}$, with $f$ as the sampling rate. Note that acceleration is only multiplied by the sampling rate once. The second multiplication is done during postprocessing.
(@) Velocity and acceleration of value zero are nudged to be 0.01.
(@) Samples with velocity above 1000 deg/s or acceleration above 100 deg/s are marked as invalid.
(@) The sample-to-sample angle is calculated as: 
$$\theta_t = atan2(\frac{y_{t+1} - y_t}{x_{t+1} - x_t}) - atan2(\frac{y_t - y_{t-1}}{x_t - x_{t-1}}).$$ 
Angles are normalized to $[0,2\pi]$ by adding $2\pi$ to negative values.
(@) Samples that have an angle with value NA are marked as invalid.
(@) The velocity, acceleration, and angle of invalid samples are set to NA.
